Bayes network classifiers for fMRI

### 2012-11-08 article/article.tex
added alineas intro

\indent Alternatively, Machine learning algorithms have been employed to learn the patterns of activity associated with some experimental condition. Subsequently, these learned patterns can be used on unseen subjects in order to predict experimental conditions from their brain activity patterns. When these predictions are accurate then it means that the identified patterns hold information about the brain activity associated with some experimental task.\\

@@

\indent Insert alinea discussing Starplus data. - related work and results\\

>>>>

\indent In fact, Machine learning algorithms have been employed to learn the patterns of activity associated with some experimental condition. Subsequently, these learned patterns can be used on unseen subjects in order to predict experimental conditions from their brain activity patterns. When these predictions are accurate then it means that the identified patterns hold information about the brain activity associated with some experimental task.\\

@@

\indent  The general goal of these machine learning studies is to identify what experimental condition a subject is in at a certain time. The state that a person is in during some trial (e.g., looking at a face) is referred to as emph{cognitive state}, because the cognitive processes that are associated with being in that state are of interest. Specifically, the aforementioned studies try to infer the cognitive state of a subject from the brain activity that is evoked in a subject by performing that trial. For example, in an experiment where subjects look at a set of pictures (e.g., a star and a plus), they would be in a certain cognitive state that is the result of looking at these pictures. One could then attempt to use machine learning on the fMRI signal that is evoked by the the brain activity associated with these cognitive states, and use this to learn for example what patterns of activity in the brain is associated with that cognitive state. This \emph{StarPlus} experiment has been performed, where in addition to viewing pictures, subjects also read sentences that contained some true or false statement about the pictures. These data have then been used to successfully infer the cognitive states of looking at either sentences or pictures within single subjects\cite{mi:2003within}, and between subjects \cite{wa:2003betw}. \\Insert alinea discussing Starplus data. - related work and results\\
